---
title: 'DECISION-MAKING ABOUT BROAD- AND NARROWCASTING: A NEUROSCIENTIFIC PERSPECTIVE'
author: "Christin Scholz, Elisa C. Baek, Matthew B. O'Donnell, Emily B. Falk"
date: "FEBRUARY, 2019"
output:
  html_document:
    highlight: textmate
    theme: paper
    toc: yes
  pdf_document:
    toc: yes
---

```{r, echo=FALSE}
library(ggplot2)
```


# Data
```{r, echo=FALSE}
# Demographics
demo<-read.csv('data/demographics.csv')

# Articles
articles<-read.csv('data/articles.csv')

# Reaction Times
rt<-read.csv('data/rt.csv',stringsAsFactors = F)

# Brain Data - Model without reaction times
nsynth_ment<-read.csv('data/ROI_extractions/nsynth_ment.csv',stringsAsFactors = F)
nsynth_self<-read.csv('data/ROI_extractions/nsynth_self.csv',stringsAsFactors = F)
nsynth_mentnotself<-read.csv('data/ROI_extractions/nsynth_mentnotself.csv',stringsAsFactors = F)
nsynth_selfnotment<-read.csv('data/ROI_extractions/nsynth_selfnotment.csv',stringsAsFactors = F)

# Brain Data - Model with reaction times
nsynth_ment_rt<-read.csv('data/ROI_extractions/nsynth_ment_rt.csv',stringsAsFactors = F)
nsynth_self_rt<-read.csv('data/ROI_extractions/nsynth_self_rt.csv',stringsAsFactors = F)
nsynth_mentnotself_rt<-read.csv('data/ROI_extractions/nsynth_mentnotself_rt.csv',stringsAsFactors = F)
nsynth_selfnotment_rt<-read.csv('data/ROI_extractions/nsynth_selfnotment_rt.csv',stringsAsFactors = F)
```


# Article task

* Reading screen presentation times: `r min(articles$pres_time)` (N = `r sum(articles$pres_time==8)`), 10 (N = `r sum(articles$pres_time==10)`) or `r max(articles$pres_time)` (N = `r sum(articles$pres_time==12)`) s

# New York Times articles 

* Article word count range: `r min(articles$total_wc)` - `r max(articles$total_wc)` words in title and abstract.

# Participants
* N = `r length(demo$pID)` 
* N (females) = `r sum(demo$gender==2)` 
* Age range: `r min(demo$age)` - `r max(demo$age)` (M = `r round(mean(demo$age),1)`, SD = `r round(sd(demo$age),1)`)

# Neural model of the article task

```{r, echo=FALSE}
# Get average reaction time for each condition per person
pIDs<-c()
content<-c()
narrow<-c()
broad<-c()
for(id in unique(rt$pID)){
  pIDs[length(pIDs)+1]<-id
  content[length(content)+1]<-mean(rt$pmod1_rt[which(rt$cond=='content' & rt$pID==id)],na.rm=T)
  narrow[length(narrow)+1]<-mean(rt$pmod1_rt[which(rt$cond=='narrowcasting' & rt$pID==id)],na.rm=T)
  broad[length(broad)+1]<-mean(rt$pmod1_rt[which(rt$cond=='broadcasting' & rt$pID==id)],na.rm=T)
}
```

* Mean reaction time 
* Control trials: M = `r mean(content)`, SD = `r sd(content)` 
* Narrowcasting trials: M = `r mean(narrow)`, SD = `r sd(narrow)`; 
* Comparison to Control: 
```{r} 
t.test(content,narrow,paired=T)
``` 
* Broadcasting trials: M = `r mean(broad)`, SD = `r sd(broad)`; 
* Comparison to Control: 
```{r} 
t.test(content,broad, paired=T)
```

* Comparison narrowcasting to broadcasting: 

```{r}
t.test(narrow,broad, paired=T)
```

#ROI analyses
Robustness checks: Relationship between Facebook friend counts and percent signal change in each contrast:

```{r}
#Broad vs. Content contrast
cor.test(nsynth_self$BROADvsCONTENT_read,demo$ego_degree)
cor.test(nsynth_ment$BROADvsCONTENT_read,demo$ego_degree)
cor.test(nsynth_selfnotment$BROADvsCONTENT_read,demo$ego_degree)
cor.test(nsynth_mentnotself$BROADvsCONTENT_read,demo$ego_degree)

#Narrow vs. Content contrast
cor.test(nsynth_self$NARROWvsCONTENT_read,demo$ego_degree)
cor.test(nsynth_ment$NARROWvsCONTENT_read,demo$ego_degree)
cor.test(nsynth_selfnotment$NARROWvsCONTENT_read,demo$ego_degree)
cor.test(nsynth_mentnotself$NARROWvsCONTENT_read,demo$ego_degree)


#Narrow vs. BROAD contrast
cor.test(nsynth_self$NARROWvsBROAD_read,demo$ego_degree)
cor.test(nsynth_ment$NARROWvsBROAD_read,demo$ego_degree)
cor.test(nsynth_selfnotment$NARROWvsBROAD_read,demo$ego_degree)
cor.test(nsynth_mentnotself$NARROWvsBROAD_read,demo$ego_degree)
```

# Results

__Figure 2b__
```{r, echo=FALSE}
# Get means of percent signal change in self and social ROIs + sds for error bars

means_self<-c(mean(nsynth_self$NARROWvsCONTENT_read),mean(nsynth_self$BROADvsCONTENT_read))
sds_self<-c(sd(nsynth_self$NARROWvsCONTENT_read),sd(nsynth_self$BROADvsCONTENT_read))

means_social<-c(mean(nsynth_ment$NARROWvsCONTENT_read),mean(nsynth_ment$BROADvsCONTENT_read))
sds_social<-c(sd(nsynth_ment$NARROWvsCONTENT_read),sd(nsynth_ment$BROADvsCONTENT_read))

means_selfnotment<-c(mean(nsynth_selfnotment$NARROWvsCONTENT_read),mean(nsynth_selfnotment$BROADvsCONTENT_read))
sds_selfnotment<-c(sd(nsynth_selfnotment$NARROWvsCONTENT_read),sd(nsynth_selfnotment$BROADvsCONTENT_read))

means_mentnotself<-c(mean(nsynth_mentnotself$NARROWvsCONTENT_read),mean(nsynth_mentnotself$BROADvsCONTENT_read))
sds_mentnotself<-c(sd(nsynth_mentnotself$NARROWvsCONTENT_read),sd(nsynth_mentnotself$BROADvsCONTENT_read))



conditions<-c('NC > C','BC > C')

data_self<-data.frame(conditions,means_self,sds_self)
data_social<-data.frame(conditions,means_social,sds_social)
data_selfnotment<-data.frame(conditions,means_selfnotment,sds_selfnotment)
data_mentnotself<-data.frame(conditions,means_mentnotself,sds_mentnotself)

# Create plots

## Self
fig2b_self<-ggplot(data_self, aes(x=as.factor(conditions), y=means_self)) +
  geom_bar(position=position_dodge(), stat="identity",fill=c('#000000','#000000'),color=c('#000000','#000000')) +
  geom_errorbar(aes(ymin=means_self-(1.96*(sds_self/sqrt(41))), ymax=means_self+(1.96*(sds_self/sqrt(41)))), width=.2,position=position_dodge(.9),color=('#646464'))+
  theme_bw() +
  labs(x = '') +
  labs(y = '') + 
  theme_bw() +
  theme(axis.text = element_text(size=16),axis.line = element_line(colour = "darkgrey"),
    panel.border = element_blank())

# Social

fig2b_social<-ggplot(data_social, aes(x=as.factor(conditions), y=means_social)) +
  geom_bar(position=position_dodge(), stat="identity",fill=c('#FFFFFF','#FFFFFF'),color=c('#000000','#000000')) +
  geom_errorbar(aes(ymin=means_social-(1.96*(sds_social/sqrt(41))), ymax=means_social+(1.96*(sds_social/sqrt(41)))), width=.2,position=position_dodge(.9))+
  theme_bw() +
  labs(x = '') +
  labs(y = '') + 
  theme_bw() +
  theme(axis.text = element_text(size=16),axis.line = element_line(colour = "darkgrey"),
    panel.border = element_blank())
```

```{r}
fig2b_self
fig2b_social
```

__COMPARISONS TO CONTROL: Results for self exclusive of social ROI__

* narrowcasting > control:  

```{r}
t.test(nsynth_selfnotment$NARROWvsCONTENT_read)
```

* broadcasting > control:  

```{r}
t.test(nsynth_selfnotment$BROADvsCONTENT_read)
```

__COMPARISONS TO CONTROL: Results for social exclusive of self ROI__

* narrowcasting > control: 
```{r}
t.test(nsynth_mentnotself$NARROWvsCONTENT_read)
```

* broadcasting > control: 
```{r}
t.test(nsynth_mentnotself$BROADvsCONTENT_read)
```

__COMPARISONS TO CONTROL: Results for model including reaction times__
```{r}
t.test(nsynth_self_rt$broadvscontent)
t.test(nsynth_self_rt$narrowvscontent)
t.test(nsynth_ment_rt$broadvscontent)
t.test(nsynth_ment_rt$narrowvscontent)
t.test(nsynth_mentnotself_rt$narrowvscontent)
t.test(nsynth_selfnotment_rt$narrowvscontent)
t.test(nsynth_mentnotself_rt$broadvscontent)
t.test(nsynth_selfnotment_rt$broadvscontent)
```

__Figure 2c__
```{r, echo=FALSE}
means<-c(mean(nsynth_self$NARROWvsBROAD_read),mean(nsynth_ment$NARROWvsBROAD_read))
sds<-c(sd(nsynth_self$NARROWvsBROAD_read),sd(nsynth_ment$NARROWvsBROAD_read))

conditions<-c('Self','Social')
data<-data.frame(conditions,means,sds)

fig2c<-ggplot(data, aes(x=as.factor(conditions), y=means)) +
  geom_bar(position=position_dodge(), stat="identity",fill=c('#000000','#FFFFFF'),color=c('#000000','#000000')) +
  geom_errorbar(aes(ymin=means-(1.96*(sds/sqrt(41))), ymax=means+(1.96*(sds/sqrt(41)))), width=.2,position=position_dodge(.9),color=c('#646464','#000000'))+
  theme_bw() +
  labs(x = '') +
  labs(y = '') + 
  theme_bw() +
  theme(axis.text = element_text(size=16),axis.line = element_line(colour = "darkgrey"),
    panel.border = element_blank())
```

```{r}
fig2c
```

__COMPARISON NARROWCASTING vs. BROADCASTING: self-related ROI__
```{r}
t.test(nsynth_self$NARROWvsBROAD_read)
```

__COMPARISON NARROWCASTING vs. BROADCASTING: self-related ROI__
```{r}
t.test(nsynth_ment$NARROWvsBROAD_read)
```

__COMPARISON NARROWCASTING vs. BROADCASTING: self exclusive of social ROI__
```{r}
t.test(nsynth_selfnotment$NARROWvsBROAD_read)
```

__COMPARISON NARROWCASTING vs. BROADCASTING: social exclusive of self ROI__
```{r}
t.test(nsynth_mentnotself$NARROWvsBROAD_read)
```

__COMPARISONS NARROWCASTING vs. BROADCASTING: Results for model including reaction times__
```{r}
t.test(nsynth_self_rt$narrowvsbroad)
t.test(nsynth_ment_rt$narrowvsbroad)
t.test(nsynth_selfnotment_rt$narrowvsbroad)
t.test(nsynth_mentnotself_rt$narrowvsbroad)
```